The title

### 2020-11-23 scripts/draft_play.Rmd

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)

BCdata <- read_excel(here("data", "bcsped_headcount.xlsx"))

@@

```{r sandbox, warning=FALSE}
library(here)
library(tidyverse)
library("readxl")

BCdatastripped_spedcat <- BCdatastripped %>% 
  mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health Impairment" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "Intensive Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
         SCHOOL_YEAR = as.factor(SCHOOL_YEAR),
         NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
         SCHOOL_YEAR = as.integer(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 7,
         SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N")

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")
#strength 1: I really like the data visualization. It is very clear! 
```

@@

bc_data_district_classification <- read_excel(here("data", "bc_data_district_classification.xlsx"))

@@

# strength 2: I really like the data cleaning part. They used pivot_longer to make the data more clear! 
```

@@

# Strength 3: Remove_empty: this function is great to remove NAs.
cleanest_primo <- cleanest_primo %>% 
  select(-six_to_twentyone_total, -x24)

@@

# This is the part the I learned. I learned the parse_number function to .This drops any non-numeric characters before or after the first number. The grouping mark specified by the locale is ignored inside the number.
```

```{r Oregon plot}

ggplot(fresh_primo, aes(age, frequency))+
  geom_line(aes(color=disability))+
  facet_wrap(~year)+
    labs(color="disability", x= "Student Age", y="Student Count", title ="Disability Prevalence By Age")

@@

```{r}
#hiding this for now
fresh_primo %>%
filter(disability=="AUTISM") %>%

ggplot(aes(age, frequency))+
 geom_line(aes(color=disability))+
facet_wrap(~year)

```
```{r}
#this is more in line with the BC graphing
ggplot(fresh_primo, aes(year, frequency))+
 geom_smooth(color = "cornflowerblue") +
 theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
 facet_wrap(~disability)+
    labs(color="frequency", x= "Year", y="Student Count", title = "Trends in Frequency")

#improvement: I am not sure what does the second ```r``` includes. maybe you could delete. 
```

>>>>

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}

library(papaja)
library(here)
library(tidyverse)
library(readxl)
library(janitor)
r_refs('r-references.bib')
#avoid using quotation marks when using library() command

library(ggplot2)
#library("ggplot2")
#why leave the two same commands?

BCdata <- read_excel(here("data", "bcsped_headcount.xlsx"))
#the best practice would be to use clean_names() and as_tibble() here, in particularly because janitor package was loaded

@@

```{r sandbox, warning=FALSE}
library(here)
library(tidyverse)
library("readxl")
#no need to load the same packages, except for "readxl"

BCdatastripped_spedcat <- BCdatastripped %>% 
  mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health Impairment" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "Intensive Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
         SCHOOL_YEAR = as.factor(SCHOOL_YEAR),
         NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
         SCHOOL_YEAR = as.integer(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 7,
         SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N")
#factoring was nicely done here!

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")

#nice visualization! It's interesting to observe the yearly trend of students with exceptionalities changes by year differently
#using the ratio of students by category instead of headcount will be more intuitive. use some nice-looking themes as well

BCdatastripped_spedcat2 <- BCdatastripped_spedcat %>%
  group_by(SCHOOL_YEAR) %>%
  mutate(total = sum(NUMBER_OF_STUDENTS)) %>% 
  mutate(ratio = NUMBER_OF_STUDENTS / total)

ggplot(BCdatastripped_spedcat2, aes(x = SCHOOL_YEAR, y = ratio)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Ratio of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Ratio") + 
   theme_minimal()

@@

bc_data_district_classification <- read_excel(here("data", "bc_data_district_classification.xlsx"))
#clean_names and as_tibble?

@@

@@

cleanest_primo <- cleanest_primo %>% 
  select(-six_to_twentyone_total, -x24)

@@

@@

```{r Oregon plot}
ggplot(fresh_primo, aes(age, frequency))+
  geom_line(aes(color=disability))+
  facet_wrap(~year)+
    labs(color="disability", x= "Student Age", y="Student Count", title ="Disability Prevalence By Age")
#nicely done as well, but it using 4 variables in one plot can be tricky. showing disability prevalence by age, but for each year would be one way to solve it

fresh_primo %>% 
  filter(year == 2002) %>% 
  ggplot(aes(age, frequency))+
  geom_line(aes(color=disability))+
  labs(color="disability", x= "Student Age", y="Student Count", title ="Disability Prevalence By Age in 2002") + 
  theme_mi

```{r}
#hiding this for now
fresh_primo %>%
  filter(disability=="AUTISM") %>%
  ggplot(aes(age, frequency)) +
  geom_line(aes(color=disability)) + 
  facet_wrap(~year)

```
```{r}
#this is more in line with the BC graphing
ggplot(fresh_primo, aes(year, frequency))+
 geom_smooth(color = "cornflowerblue", se = FALSE) +
 theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
 facet_wrap(~disability)+
    labs(color="frequency", x= "Year", y="Student Count", title = "Trends in Frequency")
#geom_smooth was used instead of geom_line because of yearly fluctuation. Were only even/odd years got recorded?

### 2020-11-23 scripts/draft_play.tex

\begin{tabular}{r|l|r}
\hline
year & disability & total\\
\hline
2002 & AUTISM & 3339\\
\hline
2002 & DEAF-BLINDNESS & 17\\
\hline
2002 & DEVELOPMENTAL DELAY & 0\\
\hline
2002 & EMOTIONAL DISTURBANCE & 4736\\
\hline
2002 & HEARING IMPAIRMENT & 873\\
\hline
2002 & INTELLECTUAL DISABILITY & 4387\\
\hline
2002 & MULTIPLE DISABILITIES & 0\\
\hline
2002 & ORTHOPEDIC IMPAIRMENT & 754\\
\hline
2002 & SPEECH OR LANGUAGE IMPAIRMENT & 15784\\
\hline
2002 & TRAUMATIC BRAIN INJURY & 306\\
\hline
2002 & VISUAL IMPAIRMENT & 297\\
\hline
2003 & AUTISM & 3759\\
\hline
2003 & DEAF-BLINDNESS & 17\\
\hline
2003 & DEVELOPMENTAL DELAY & 0\\
\hline
2003 & EMOTIONAL DISTURBANCE & 4597\\
\hline
2003 & HEARING IMPAIRMENT & 811\\
\hline
2003 & INTELLECTUAL DISABILITY & 4351\\
\hline
2003 & MULTIPLE DISABILITIES & 0\\
\hline
2003 & ORTHOPEDIC IMPAIRMENT & 749\\
\hline
2003 & SPEECH OR LANGUAGE IMPAIRMENT & 15642\\
\hline
2003 & TRAUMATIC BRAIN INJURY & 300\\
\hline
2003 & VISUAL IMPAIRMENT & 295\\
\hline
2004 & AUTISM & 4341\\
\hline
2004 & DEAF-BLINDNESS & 12\\
\hline
2004 & DEVELOPMENTAL DELAY & 0\\
\hline
2004 & EMOTIONAL DISTURBANCE & 4661\\
\hline
2004 & HEARING IMPAIRMENT & 809\\
\hline
2004 & INTELLECTUAL DISABILITY & 4334\\
\hline
2004 & MULTIPLE DISABILITIES & 0\\
\hline
2004 & ORTHOPEDIC IMPAIRMENT & 741\\
\hline
2004 & SPEECH OR LANGUAGE IMPAIRMENT & 15627\\
\hline
2004 & TRAUMATIC BRAIN INJURY & 286\\
\hline
2004 & VISUAL IMPAIRMENT & 325\\
\hline
2005 & AUTISM & 4810\\
\hline
2005 & DEAF-BLINDNESS & 14\\
\hline
2005 & DEVELOPMENTAL DELAY & 0\\
\hline
2005 & EMOTIONAL DISTURBANCE & 4661\\
\hline
2005 & HEARING IMPAIRMENT & 799\\
\hline
2005 & INTELLECTUAL DISABILITY & 4218\\
\hline
2005 & MULTIPLE DISABILITIES & 0\\
\hline
2005 & ORTHOPEDIC IMPAIRMENT & 738\\
\hline
2005 & SPEECH OR LANGUAGE IMPAIRMENT & 15833\\
\hline
2005 & TRAUMATIC BRAIN INJURY & 273\\
\hline
2005 & VISUAL IMPAIRMENT & 301\\
\hline
2006 & AUTISM & 5459\\
\hline
2006 & DEAF-BLINDNESS & 12\\
\hline
2006 & DEVELOPMENTAL DELAY & 0\\
\hline
2006 & EMOTIONAL DISTURBANCE & 4662\\
\hline
2006 & HEARING IMPAIRMENT & 812\\
\hline
2006 & INTELLECTUAL DISABILITY & 4193\\
\hline
2006 & MULTIPLE DISABILITIES & 0\\
\hline
2006 & ORTHOPEDIC IMPAIRMENT & 742\\
\hline
2006 & SPEECH OR LANGUAGE IMPAIRMENT & 15956\\
\hline
2006 & TRAUMATIC BRAIN INJURY & 269\\
\hline
2006 & VISUAL IMPAIRMENT & 302\\
\hline
2007 & AUTISM & 6071\\
\hline
2007 & DEAF-BLINDNESS & 21\\
\hline
2007 & DEVELOPMENTAL DELAY & 0\\
\hline
2007 & EMOTIONAL DISTURBANCE & 4631\\
\hline
2007 & HEARING IMPAIRMENT & 835\\
\hline
2007 & INTELLECTUAL DISABILITY & 4121\\
\hline
2007 & MULTIPLE DISABILITIES & 0\\
\hline
2007 & ORTHOPEDIC IMPAIRMENT & 745\\
\hline
2007 & SPEECH OR LANGUAGE IMPAIRMENT & 16046\\
\hline
2007 & TRAUMATIC BRAIN INJURY & 258\\
\hline
2007 & VISUAL IMPAIRMENT & 325\\
\hline
2008 & AUTISM & 6571\\
\hline
2008 & DEAF-BLINDNESS & 15\\
\hline
2008 & DEVELOPMENTAL DELAY & 0\\
\hline
2008 & EMOTIONAL DISTURBANCE & 4671\\
\hline
2008 & HEARING IMPAIRMENT & 823\\
\hline
2008 & INTELLECTUAL DISABILITY & 4012\\
\hline
2008 & MULTIPLE DISABILITIES & 0\\
\hline
2008 & ORTHOPEDIC IMPAIRMENT & 746\\
\hline
2008 & SPEECH OR LANGUAGE IMPAIRMENT & 16116\\
\hline
2008 & TRAUMATIC BRAIN INJURY & 279\\
\hline
2008 & VISUAL IMPAIRMENT & 317\\
\hline
2009 & AUTISM & 7012\\
\hline
2009 & DEAF-BLINDNESS & 8\\
\hline
2009 & DEVELOPMENTAL DELAY & 0\\
\hline
2009 & EMOTIONAL DISTURBANCE & 4669\\
\hline
2009 & HEARING IMPAIRMENT & 830\\
\hline
2009 & INTELLECTUAL DISABILITY & 4000\\
\hline
2009 & MULTIPLE DISABILITIES & 0\\
\hline
2009 & ORTHOPEDIC IMPAIRMENT & 713\\
\hline
2009 & SPEECH OR LANGUAGE IMPAIRMENT & 16132\\
\hline
2009 & TRAUMATIC BRAIN INJURY & 283\\
\hline
2009 & VISUAL IMPAIRMENT & 314\\
\hline
2010 & AUTISM & 7357\\
\hline
2010 & DEAF-BLINDNESS & 8\\
\hline
2010 & DEVELOPMENTAL DELAY & -144\\
\hline
2010 & EMOTIONAL DISTURBANCE & 4638\\
\hline
2010 & HEARING IMPAIRMENT & 827\\
\hline
2010 & INTELLECTUAL DISABILITY & 3926\\
\hline
2010 & MULTIPLE DISABILITIES & -144\\
\hline
2010 & ORTHOPEDIC IMPAIRMENT & 718\\
\hline
2010 & SPEECH OR LANGUAGE IMPAIRMENT & 16354\\
\hline
2010 & TRAUMATIC BRAIN INJURY & 271\\
\hline
2010 & VISUAL IMPAIRMENT & 312\\
\hline
2011 & AUTISM & 7618\\
\hline
2011 & DEAF-BLINDNESS & 12\\
\hline
2011 & DEVELOPMENTAL DELAY & -36\\
\hline
2011 & EMOTIONAL DISTURBANCE & 4567\\
\hline
2011 & HEARING IMPAIRMENT & 810\\
\hline
2011 & INTELLECTUAL DISABILITY & 3830\\
\hline
2011 & MULTIPLE DISABILITIES & -144\\
\hline
2011 & ORTHOPEDIC IMPAIRMENT & 738\\
\hline
2011 & SPEECH OR LANGUAGE IMPAIRMENT & 16206\\
\hline
2011 & TRAUMATIC BRAIN INJURY & 268\\
\hline
2011 & VISUAL IMPAIRMENT & 313\\
\hline
2012 & AUTISM & 7888\\
\hline
2012 & DEAF-BLINDNESS & 10\\
\hline
2012 & DEVELOPMENTAL DELAY & -54\\
\hline
2012 & EMOTIONAL DISTURBANCE & 4524\\
\hline
2012 & HEARING IMPAIRMENT & 810\\
\hline
2012 & INTELLECTUAL DISABILITY & 3847\\
\hline
2012 & MULTIPLE DISABILITIES & -144\\
\hline
2012 & ORTHOPEDIC IMPAIRMENT & 705\\
\hline
2012 & SPEECH OR LANGUAGE IMPAIRMENT & 15938\\
\hline
2012 & TRAUMATIC BRAIN INJURY & 256\\
\hline
2012 & VISUAL IMPAIRMENT & 300\\
\hline
2013 & AUTISM & 8021\\
\hline
2013 & DEAF-BLINDNESS & 9\\
\hline
2013 & DEVELOPMENTAL DELAY & -36\\
\hline
2013 & EMOTIONAL DISTURBANCE & 4526\\
\hline
2013 & HEARING IMPAIRMENT & 830\\
\hline
2013 & INTELLECTUAL DISABILITY & 3847\\
\hline
2013 & MULTIPLE DISABILITIES & -144\\
\hline
2013 & ORTHOPEDIC IMPAIRMENT & 700\\
\hline
2013 & SPEECH OR LANGUAGE IMPAIRMENT & 16077\\
\hline
2013 & TRAUMATIC BRAIN INJURY & 254\\
\hline
2013 & VISUAL IMPAIRMENT & 288\\
\hline
2014 & AUTISM & 8364\\
\hline
2014 & DEAF-BLINDNESS & 5\\
\hline
2014 & DEVELOPMENTAL DELAY & -36\\
\hline
2014 & EMOTIONAL DISTURBANCE & 4577\\
\hline
2014 & HEARING IMPAIRMENT & 851\\
\hline
2014 & INTELLECTUAL DISABILITY & 3874\\
\hline
2014 & MULTIPLE DISABILITIES & -144\\
\hline
2014 & ORTHOPEDIC IMPAIRMENT & 673\\
\hline
2014 & SPEECH OR LANGUAGE IMPAIRMENT & 16236\\
\hline
2014 & TRAUMATIC BRAIN INJURY & 248\\
\hline
2014 & VISUAL IMPAIRMENT & 296\\
\hline
2015 & AUTISM & 8665\\
\hline
2015 & DEAF-BLINDNESS & 5\\
\hline
2015 & DEVELOPMENTAL DELAY & -36\\
\hline
2015 & EMOTIONAL DISTURBANCE & 4704\\
\hline
2015 & HEARING IMPAIRMENT & 844\\
\hline
2015 & INTELLECTUAL DISABILITY & 3951\\
\hline
2015 & MULTIPLE DISABILITIES & -144\\
\hline
2015 & ORTHOPEDIC IMPAIRMENT & 649\\
\hline
2015 & SPEECH OR LANGUAGE IMPAIRMENT & 16294\\
\hline
2015 & TRAUMATIC BRAIN INJURY & 240\\
\hline
2015 & VISUAL IMPAIRMENT & 291\\
\hline
2016 & AUTISM & 8940\\
\hline
2016 & DEAF-BLINDNESS & 8\\
\hline
2016 & DEVELOPMENTAL DELAY & 0\\
\hline
2016 & EMOTIONAL DISTURBANCE & 4944\\
\hline
2016 & HEARING IMPAIRMENT & 829\\
\hline
2016 & INTELLECTUAL DISABILITY & 4058\\
\hline
2016 & MULTIPLE DISABILITIES & -144\\
\hline
2016 & ORTHOPEDIC IMPAIRMENT & 624\\
\hline
2016 & SPEECH OR LANGUAGE IMPAIRMENT & 16075\\
\hline
2016 & TRAUMATIC BRAIN INJURY & 261\\
\hline
2016 & VISUAL IMPAIRMENT & 306\\
\hline
2017 & AUTISM & 9288\\
\hline
2017 & DEAF-BLINDNESS & 12\\
\hline
2017 & DEVELOPMENTAL DELAY & 0\\
\hline
2017 & EMOTIONAL DISTURBANCE & 5122\\
\hline
2017 & HEARING IMPAIRMENT & 841\\
\hline
2017 & INTELLECTUAL DISABILITY & 4103\\
\hline
2017 & MULTIPLE DISABILITIES & -144\\
\hline
2017 & ORTHOPEDIC IMPAIRMENT & 612\\
\hline
2017 & SPEECH OR LANGUAGE IMPAIRMENT & 16087\\
\hline
2017 & TRAUMATIC BRAIN INJURY & 282\\
\hline
2017 & VISUAL IMPAIRMENT & 282\\
\hline
2018 & AUTISM & 9752\\
\hline
2018 & DEAF-BLINDNESS & 11\\
\hline
2018 & DEVELOPMENTAL DELAY & -36\\
\hline
2018 & EMOTIONAL DISTURBANCE & 5286\\
\hline
2018 & HEARING IMPAIRMENT & 848\\
\hline
2018 & INTELLECTUAL DISABILITY & 4167\\
\hline
2018 & MULTIPLE DISABILITIES & -144\\
\hline
2018 & ORTHOPEDIC IMPAIRMENT & 602\\
\hline
2018 & SPEECH OR LANGUAGE IMPAIRMENT & 16357\\
\hline
2018 & TRAUMATIC BRAIN INJURY & 294\\
\hline
2018 & VISUAL IMPAIRMENT & 269\\
\hline
2019 & AUTISM & 10290\\
\hline
2019 & DEAF-BLINDNESS & 21\\
\hline
2019 & DEVELOPMENTAL DELAY & 266\\
\hline
2019 & EMOTIONAL DISTURBANCE & 5568\\
\hline
2019 & HEARING IMPAIRMENT & 870\\
\hline
2019 & INTELLECTUAL DISABILITY & 4199\\
\hline
2019 & MULTIPLE DISABILITIES & -144\\
\hline
2019 & ORTHOPEDIC IMPAIRMENT & 562\\
\hline
2019 & SPEECH OR LANGUAGE IMPAIRMENT & 16423\\
\hline
2019 & TRAUMATIC BRAIN INJURY & 327\\
\hline
2019 & VISUAL IMPAIRMENT & 282\\
\hline
\end{tabular}

@@

@@

\includegraphics{draft_play_files/figure-latex/unnamed-chunk-3-1.pdf}

@@

We used R (Version 3.6.1; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

@@

@@

>>>>

@@

\includegraphics{draft_play_files/figure-latex/unnamed-chunk-1-1.pdf}

@@

@@

We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{dplyr} (Version 1.0.2; Wickham et al., 2020), \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 2.0.1; Firke, 2020), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.3; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019) for all our analyses.

@@

\leavevmode\hypertarget{ref-R-janitor}{}%
Firke, S. (2020). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\hypertarget{ref-R-here}{}%
Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}

@@

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the tidyverse. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-readxl}{}%
Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
